Learning by Teaching a Robot:\\The Case of Handwriting

### 2015-12-16 main.tex
WIP on the Normandy study

\usepackage{xspace}
\newcommand{\eg}{\textit{e.g.}\xspace}
\newcommand{\etal}{\textit{et al.}\xspace}
\newcommand{\ie}{\textit{i.e.}\xspace}
\newcommand{\etc}{\textit{etc.}\xspace}
\newcommand{\vs}{\textit{vs.}\xspace}

@@

@@

\begin{table}
    \centering
    \begin{tabular}{cccccc}
        \toprule
        Child          & \# demos & \# positive & \# negative & $p_{robot}$ & $p_{child}$\\ \midrule
        \emph{Valérie} & 127 & 24 & 6 & $< .003$ \tt ** & $< .055$ \tt .\\ 
        \emph{Émilien} & 223 & 20 & 9 & $.17$ \it ns & $.35$ \it ns \\
        \emph{Mathieu} & 131 & 10 & 3 & $< .004$ \tt ** & $< .008$ \tt **\\
        \emph{Johan}   & 98 & 10 & 5 &  $.15$ \it ns & $.38$ \it ns  \\
        \emph{Nicolas} & 115 & 16 & 4 & $< .0006$ \tt *** & $< .003$ \tt ** \\
        \emph{Antoine} & 83 & 10 & 3 & $< .031$ \tt * & $.6$ \it ns \\
        \emph{Adèle}   & 35 & 4 & 2 & $< .05$ \tt * & $< .04$ \tt * \\
        \emph{Marie}   & 40 & 5 & 1 &  $.54$ \it ns & $.2$ \it ns \\ \midrule
        Total          & 852 & 99 & 33 &   & \\ \bottomrule
    \end{tabular}
    \caption{\small results of evaluations. demo: number of demonstrations provided by
        the child over all session. rew: number of rewards accorded by
        the child. pun: number of punishments. p(robot): are the evaluations
        significantly corresponding to the progression of the robot ? p(child): are the
        evaluations significantly corresponding to the child's own
progression ?}
    \label{table:scores}
\end{table}

To study a possible correlation between the children's feedback and the robot's
improvements, estimated the robot's progress as the difference between an
initial score (average euclidian distance between the shape drawn by the robot
at its first attempt and the shape of the reference letter) and the robot's
score at the current round of demonstrations.

Let $P_i$ be the estimated progression of the robot at time $ i$. Of course, if
the child chose to switch to a new word at time $ j$ , we have $ P_{j}=0$ and
clearly $ P_0=0$.  To measure whether the fact that the child was rewarding the
robot when it was progressing was significant or not, we generated 10000 times
the same number of reward/punishment but accorded at random times. Let $ R_i^n$
be the $n^{th}$ generated evaluation at time $ i$ ($ R_i^n = 0$ if no evaluation
occurred at time $ i$ , $ R_i^n=1$ if a reward occurred at time $i$ and
$R_i^n=-1$ if a punishment occurred at time $i$), and $\overline{R}_i$ be the
actual evaluation at time $i$. For each $n^{th}$ generated sequence of
evaluation, we compute a score of evaluation: $$ S^n = \sum\limits_i{R_i^n
P_i}$$ Then we can estimate the p-value $p$ of the actual score: $$ \overline{S}
= \sum\limits_i{\overline{R}_i P_i}$$ given the distribution of the generated
scores $\left(S^n\right)_n$, which is assumed to be Gaussian:

$$
p(\overline{S})= \mathbb{P}{\left[X>\overline{S}\right]} = 1-\phi{\left(\frac{\overline{S}-\mu}{\sigma}\right)}
$$

where $\phi$ denotes the cumulative distribution function of the standard normal
distribution, $\mu$ the mean and $\sigma$ the deviation of the generated scores
$\left(S^n\right)_n$.  As a result, we found that 5 of the 8 children obtained a
score of evaluation significantly hight ($p(\overline{S})<0.05$). Score of
evaluation p-values of each child is reported in the second-to-last column of
Table~\ref{table:scores}.

We also studied correlation between children's evaluations and their own
progression. The analysis was conducted in the same way, using distances between
children demonstrations and reference allographs to compute children
progressions.  3 of 5 children that played ``seriously" obtained score of
evaluation of their own progression significantly high (last column of
Table~\ref{table:scores}). For those children, it seems that the robot was
reflecting their own performances, and while they were judging the robot
positively (three times more rewards than punishments) they were actually
evaluating themselves.

>>>>

\usepackage{xspace}
\newcommand{\eg}{\textit{e.g.}\xspace}
\newcommand{\etal}{\textit{et al.}\xspace}
\newcommand{\ie}{\textit{i.e.}\xspace}
\newcommand{\etc}{\textit{etc.}\xspace}
\newcommand{\vs}{\textit{vs.}\xspace}
\newcommand{\resp}{\textit{resp.}\xspace}

@@

\begin{table}
    \centering
    \begin{tabular}{ccccll}
        \toprule
        Child          & \#demos & \#positive & \#negative & $r_{robot}$ & \\ \midrule
        \emph{Valérie} & 127 & 24 & 6 & 0.25 \small\tt **  \\ 
        \emph{Émilien} & 223 & 20 & 9 & 0.06 \small\it ns  \\
        \emph{Mathieu} & 131 & 10 & 3 & 0.23 \small\tt **  \\
        \emph{Nicolas} & 115 & 16 & 4 & 0.31 \small\tt *** \\
        \emph{Johan}   & 98 & 10 & 5  & 0.10 \small\it ns  \\
        \emph{Antoine} & 83 & 10 & 3  & 0.20 \small\tt *   \\
        \emph{Adèle}   & 35 & 4 & 2   & 0.28 \small\tt *   \\
        \emph{Marie}   & 40 & 5 & 1   & -0.02 \small\it ns \\ \midrule
        Total          & 852 & 99 & 33  &   & \\ \bottomrule
    \end{tabular}
    \caption{\small Feedback from the children to the robot. \emph{\#demos}
        denotes the total number of demonstrations drawn by the children;
        \emph{\#positive} and \emph{\#negative} the number of positive \resp
        negative feedbacks they provided. $r_{robot}$ reflects the correlation
        between the feedback provided by the children and the performance of the
        robot. Results taken from~\cite{jacq2016building}.}

    \label{table:scores}
\end{table}

@@

To study the correlation between the children's feedback and the robot's
actual improvements, we estimate the robot's progress as the difference between an
initial score (average euclidian distance between the shape drawn by the robot
at its first attempt and the shape of the reference letter) and the robot's
score at the current round of demonstrations. We then correlate this progress
to the positive or negative feedback provided by the children, following a
statistical method presented in~\cite{jacq2016building}.

We find (Table~\ref{table:scores}) that the feedback of five out of the eight
children do significantly correlate with the actual performance of the robot:
this indicates that these children are effectively taking on the teacher's
clothes and are seriously providing feedback to the robot. \fixme{what can we
say about the 3 others? they did not play seriously, or they were unable to
actually recognize the robot mistakes?}
